### 2020-10-22 old/full_version_1013/conclusions.tex
reorg

This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
We validated our theory and conducted further studies on text classification tasks.
We describe several open questions for future work.
%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
%Second, it would be interesting to extend our result to classification problems such as logistic regression.
First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \citet{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.

>>>>

This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
We provided tight generalization bounds that scale with dataset properties such as their sample sizes and covariate shifts.
Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
We validated our results and conducted further studies on a real world classification task.

We describe several open questions for future work.
First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic random matrices.
This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.  
%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \cite{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-22 old/writeup/app_exp.tex
reorg

\subsection{Missing Details from the Experiments}\label{app_experiments}

@@

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
	\label{fig_covariate_app}
\end{figure}

>>>>

\section{Missing Details from the Experiments}\label{app_experiments}

@@

\begin{figure}%[!t]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
	\label{fig_covariate_app}
\end{figure}

### 2020-10-22 old/writeup/proof_extension.tex
reorg

	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
	\begin{align*}
		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
	\end{align*}
	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
Combining the above two estimates, we conclude the proof.
\end{proof}
%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
%\begin{itemize}
%	\item The de-noising effect of multi-task learning.
%	\item Multi-task training vs single-task training can be either positive or negative.
%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
%\end{itemize}

>>>>

	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
	\begin{align*}
		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
	\end{align*}
	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
	$$\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
Combining the above two estimates, we conclude the proof.
\end{proof}
%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
%\begin{itemize}
%	\item The de-noising effect of multi-task learning.
%	\item Multi-task training vs single-task training can be either positive or negative.
%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
%\end{itemize}
